Methodology for Assessing the State of the Practice for Domain X

### 2020-12-03 StateOfPractice/Methodology/Methodology.tex
removed old note
Beginning of some additional content for the introduction - still need to add refs to bib, need to complete into

@@

\section{Using Data to Rank Family Members}

Describe AHP process (or similar).

>>>>

Research software involves using scientific computing tools to simulate
mathematical models of real world systems so that we can better understand and
predict the system's behaviour.  A small sample of some important examples of
research software include the following: designing new automotive parts,
analysing the flow of blood in the body, and determining the concentration of a
pollutant released into the groundwater.  As these examples illustrate, research
software can be used for tackling problems that impact such areas as
manufacturing, financial planning, environmental policy, and the health, welfare
and safety of communities.

The challenging.  Room for improvement.  SEI, BME.  Problem in that current
state-of-the-practice for research software does not incorporate
state-of-the-art SE tools and methods \citep{JohansonAndHasselbring2018}.  The
lack of SE tools and methods is viewed as contributing to sustainability and
reliability problems \citep{FaulkEtAl2009}.  Embarrassing failures have
occurred, like a retraction of derived molecular protein structures
\citep{Miller2006} and fixing and then reintroducing the same error in a large
code base three times in 20 year \citep{MilewiczAndRaybourn2018}.  To improve
this situation, we need to more fully understand the current state of the
practice for research software.

@@
